R for Clinical Study Reports and Submission

### 2023-06-05 submission-environment.qmd
Add Quarto PDF output - magically working without tuning

::: {.rmdnote data-latex=""}
As of Q4 2021, the cleanslate package used in this chapter
is still under active development and validation.
This chapter gives a preview of the planned APIs.
They may change in the future.
:::

@@

- Create a project folder under `C:/temp/` with a `.Rproj` file;
- Download R `4.1.1` installer from CRAN, and install it into `C:/temp/R/`;
- Not install Rtools (by default, `rtools_version = NULL`);
- Create a `.Rprofile` file under the project folder, set `options(repos)`
  to use the specified `repo` (an MRAN snapshot in this example),
  and give instruction to set the R binary path in RStudio;
- Create a `.Renviron` file under the project folder and set the
  library path to be the library of the project-specific R installation.

@@

Go to the working directory created above, double click the .Rproj file
to open the project in RStudio. Follow the instructions to select the
project-specific R version, then restart RStudio. If successful,
the R version and package repo should be printed as defined above.

@@

To make it convenient to use cleanslate in experiments,
one can also use its RStudio addin. After cleanslate
is installed, click `Addins` -> `cleanslate` -> `Create portable R environment`
in RStudio, or call `cleanslate:::create_env_addin()` to open it.

>>>>

::: {.callout-note}
As of Q4 2021, the cleanslate package used in this chapter
is still under active development and validation.
This chapter gives a preview of the planned APIs.
They may change in the future.
:::

@@

- Create a project folder under `C:/temp/` with a `.Rproj` file;
- Download R `4.1.1` installer from CRAN, and install it into `C:/temp/R/`;
- Not install Rtools (by default, `rtools_version = NULL`);
- Create a `.Rprofile` file under the project folder, set `options(repos)`
  to use the specified `repo` (an MRAN snapshot in this example),
  and give instruction to set the R binary path in RStudio IDE;
- Create a `.Renviron` file under the project folder and set the
  library path to be the library of the project-specific R installation.

@@

Go to the working directory created above, double click the .Rproj file
to open the project in RStudio IDE. Follow the instructions to select the
project-specific R version, then restart RStudio IDE. If successful,
the R version and package repo should be printed as defined above.

@@

To make it convenient to use cleanslate in experiments,
one can also use its RStudio IDE addin. After cleanslate
is installed, click `Addins` -> `cleanslate` -> `Create portable R environment`
in RStudio IDE, or call `cleanslate:::create_env_addin()` to open it.
